---
title: "Data Exploration and Unsupervised Learning"
author: "Arpita Shah"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Step 0 - Load the required libraries

```{r load libraries, warning=FALSE, message=FALSE}
library(readr)
library(tidytext)
library(tidyverse)
library(ngram)
library(wordcloud2)
library(htmlwidgets)
library(webshot)
library(ggraph)
library(igraph)
library(tm)
library(topicmodels)
```

## Step 1 - Loading the processed data

```{r load data, warning=FALSE, message=FALSE}
hm_data <- read_csv("../output/processed_moments.csv")
```

```{r add word count, warning=FALSE, message=FALSE}
hm_data <- hm_data %>%
  select(wid, 
         reflection_period,
         ground_truth_category,
         predicted_category,
         id,
         text) %>%
  
  # Counting the remaining number of words in each happy moment
  mutate(count = sapply(hm_data$text, wordcount))

summary(hm_data$count)
```

## Step 2 - Visualize the most frequent occurences. Here we count individual words as well as bigrams.

### Individual terms

```{r tokenize words, warning=FALSE, message=FALSE}
# Tokenizing individual word from happy moments
bag_of_words <-  hm_data %>%
  unnest_tokens(word, text)

# Counting the frequency of each token
word_count <- bag_of_words %>%
  count(word, sort = TRUE)
```

#### Bar Chart

```{r overall barchart, warning=FALSE, message=FALSE}
# Visualize the words with frequency greater than 2500 in the corpus
word_count %>%
  filter(n > 2500) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  ylab("Word Frequency")+
  coord_flip()

ggsave("../figs/Most_frequent_terms_barchart.png",
       width = 8, height = 6)
```

#### Word Cloud

```{r overall wordcloud, warning=FALSE, message=FALSE}
#webshot::install_phantomjs()

# Visualize the top 50 words in terms of frequency
wc <- word_count %>%
  slice(1:50) %>%
  wordcloud2(size = 0.75,
             rotateRatio = 0.4,
             minRotation = pi/2,
             maxRotation = pi/2,
             color = "random-light",
             backgroundColor = "black")

saveWidget(wc, "../figs/overall_wordcloud.html", selfcontained = FALSE)
webshot::webshot("../figs/overall_wordcloud.html",
                 "../figs/overall_wordcloud.png",
                 vwidth = 800, vheight = 600,
                 delay = 30)

```

### Bigrams

```{r creating bigrams, warning=FALSE, message=FALSE}
# Tokenize happy moments into bigrams
hm_bigrams <- hm_data %>%
  filter(count != 1) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)
```

##### Network graph

```{r create graph object, warning=FALSE, message=FALSE}
# Count the number of bigrams
bigram_counts <- hm_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  count(word1, word2, sort = TRUE)

# Create a graph object with edges going from first word in the bigram to the second word
bigram_graph <- bigram_counts %>%
  filter(n > 100) %>%
  graph_from_data_frame()

bigram_graph
```

```{r network graph, warning=FALSE, message=FALSE}
# Visualize the bigrams as a network graph
set.seed(123)

a <- grid::arrow(type = "closed", length = unit(.1, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.05, 'inches')) +
  geom_node_point(color = "skyblue", size = 3) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void()

ggsave("../figs/Most_frequent_bigram.png",
       width = 8, height = 6)
```

## Step 3 - After exploratory data analysis, we train unsupervised learning algorithms on the collection of happy moments for Information Retrieval. We first do hard clustering using K-Means algorithm and then soft clustering using topic modeling.

### K-means Clustering

```{r create dtm, warning=FALSE, message=FALSE}
# Treat each happy moment as a document
# Creating a Document-Term Matrix with words that appear in at least 1% of the documents
corpus <- VCorpus(VectorSource(hm_data$text))
ndocs <- length(corpus)

minTermFreq <- ndocs * 0.01
maxTermFreq <- Inf

dtm <- DocumentTermMatrix(corpus,
                          control = list(
                                bounds = list(global = c(minTermFreq, maxTermFreq))
                              ))

inspect(dtm)
```

```{r kmeans cluster, warning=FALSE, message=FALSE}
# Calculating TF-IDF from Document-Term Matrix 
dtm_tfidf <- weightTfIdf(dtm, normalize = TRUE)

# K-means clustering with 7 clusters
cl <- kmeans(as.matrix(dtm_tfidf), 7, nstart = 20, iter.max = 25)

# Frequency of cluster assignments
table(cl$cluster)
```

```{r join clusters with data, warning=FALSE, message=FALSE}
# Updating happy moment ID
hm_data <- hm_data %>%
  mutate(updated_id = row_number())

# Attaching cluster labels to the documents
cluster_id <- tibble(cl$cluster) %>%
  rename(cluster_id = 'cl$cluster') %>%
  mutate(updated_id = row_number()) %>%
  right_join(hm_data) %>%
  select(updated_id, cluster_id, text)
```

```{r overall cluster distribution, warning=FALSE, message=FALSE}
# Exploring distribution of words in each cluster
cluster_words <- cluster_id %>%
  unnest_tokens(word, text) %>%
  count(cluster_id, word, sort = TRUE)

# Top 10 words in each cluster
cluster_words %>%
  group_by(cluster_id) %>%
  mutate(word = reorder(word, n)) %>%
  top_n(10, n) %>%
  ggplot(aes(word, n, fill = as.factor(cluster_id))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~as.factor(cluster_id), scales = "free") +
  coord_flip()

ggsave("../figs/Most_frequent_terms_per_cluster.png",
       width = 8, height = 6)
```

```{r cluster wordclouds, warning=FALSE, message=FALSE}
# Ignoring the top 2 words from each cluster to handle the size of words
# for interpretation and then creating word clouds
wordcloud <- function(data, cluster_num, limit) {
  
  data %>%
  filter(cluster_id == cluster_num) %>%
  select(-cluster_id) %>%
  slice(3:limit) %>%
  wordcloud2(size = 0.75,
             rotateRatio = 0.4,
             minRotation = pi/2,
             maxRotation = pi/2,
             color = "random-light",
             backgroundColor = "black")
}

# Word cloud for each cluster
wc1 <- wordcloud(data = cluster_words, cluster_num = 1, limit = 50)
saveWidget(wc1, "../figs/wordcloud_cluster1.html", selfcontained = FALSE)
webshot::webshot("../figs/wordcloud_cluster1.html",
                 "../figs/wordcloud_cluster1.png",
                 vwidth = 800, vheight = 600,
                 delay = 30)

wc2 <- wordcloud(data = cluster_words, cluster_num = 2, limit = 50)
saveWidget(wc2, "../figs/wordcloud_cluster2.html", selfcontained = FALSE)
webshot::webshot("../figs/wordcloud_cluster2.html",
                 "../figs/wordcloud_cluster2.png",
                 vwidth = 800, vheight = 600,
                 delay = 30)

wc3 <- wordcloud(data = cluster_words, cluster_num = 3, limit = 50)
saveWidget(wc3, "../figs/wordcloud_cluster3.html", selfcontained = FALSE)
webshot::webshot("../figs/wordcloud_cluster3.html",
                 "../figs/wordcloud_cluster3.png",
                 vwidth = 800, vheight = 600,
                 delay = 30)

wc4 <- wordcloud(data = cluster_words, cluster_num = 4, limit = 50)
saveWidget(wc4, "../figs/wordcloud_cluster4.html", selfcontained = FALSE)
webshot::webshot("../figs/wordcloud_cluster4.html",
                 "../figs/wordcloud_cluster4.png",
                 vwidth = 800, vheight = 600,
                 delay = 30)

wc5 <- wordcloud(data = cluster_words, cluster_num = 5, limit = 50)
saveWidget(wc5, "../figs/wordcloud_cluster5.html", selfcontained = FALSE)
webshot::webshot("../figs/wordcloud_cluster5.html",
                 "../figs/wordcloud_cluster5.png",
                 vwidth = 800, vheight = 600,
                 delay = 30)

wc6 <- wordcloud(data = cluster_words, cluster_num = 6, limit = 50)
saveWidget(wc6, "../figs/wordcloud_cluster6.html", selfcontained = FALSE)
webshot::webshot("../figs/wordcloud_cluster6.html",
                 "../figs/wordcloud_cluster6.png",
                 vwidth = 800, vheight = 600,
                 delay = 30)

wc7 <- wordcloud(data = cluster_words, cluster_num = 7, limit = 50)
saveWidget(wc7, "../figs/wordcloud_cluster7.html", selfcontained = FALSE)
webshot::webshot("../figs/wordcloud_cluster7.html",
                 "../figs/wordcloud_cluster7.png",
                 vwidth = 800, vheight = 600,
                 delay = 30)
```

### Topic Modeling

```{r drop empty documents, warning=FALSE, message=FALSE}
# Removing empty documents
dtm.new <- dtm[rowSums(as.matrix(dtm))>0, ]
dtm.new
```

```{r topic model, warning=FALSE, message=FALSE}
# Topic modeling for 7 topics
lda <- LDA(dtm.new, k = 7, control = list(seed = 12345))
```

```{r beta matrix, warning=FALSE, message=FALSE}
# Beta - per topic, per word probabilities
topics <- tidy(lda, matrix = "beta")
topics
```

```{r topic distribution, warning=FALSE, message=FALSE}
# Top 10 words in each topic based on their beta values
top_terms <- topics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()

ggsave("../figs/Most_frequent_terms_per_topic.png",
       width = 8, height = 6)
```

```{r beta spread, warning=FALSE, message=FALSE}
# Exploring what separates one topic from the other
beta_spread <- topics %>%
  mutate(topic = paste0("topic", topic)) %>%
  spread(topic, beta) %>%
  filter(topic3 > .001 | topic5 > .001) %>%
  mutate(log_ratio = log2(topic3 / topic5))

beta_spread %>%
  group_by(direction = log_ratio > 0) %>%
  top_n(10, abs(log_ratio)) %>%
  ungroup() %>%
  mutate(term = reorder(term, log_ratio)) %>%
  ggplot(aes(term, log_ratio)) +
  geom_col() +
  labs(y = "Log2 ratio of beta in topic 3 / topic 5") +
  coord_flip()

ggsave("../figs/topic3_vs_topic5.png",
       width = 8, height = 6)

# Similarly, we can explore the differences between other topics as well

# However, k-means clustering seems to be doing a better job at clustering similar
# documents here when compared to topic modeling
```